High-level cognition is supported by at least second order dynamic correlations in neural activity patterns

### 2019-08-30 paper/main.tex
working on parameter robustness testing section

\subsubsection*{Feature selection and testing}
We sought to examine which types of neural features (i.e.,
activations, first-order dynamic correlations, and higher-order
dynamic correlations) were informative to the temporal decoders.
Using the notation above, these features correspond to $\mathbf{Y}_0$,
$\mathbf{X}_1$, $\mathbf{X}_2$, $\mathbf{X}_3$, and so on (we examined
up to tenth order correlations, or $\mathbf{X}_{10}$).

@@

After estimating an optimal set of weights, we computed a new set of
$n + 1$ $\mathbf{\Lambda}$ matrices correlating timepoints from  $\mathcal{G}_{\mathrm{train}}$
and $\mathcal{G}_{\mathrm{test}}$.

\textbf{JRM STOPPED HERE}--
say something about delta function kernel to avoid something at higher
orders, then in the last order use a gaussian, laplace, or mexican hat kernel.

compute lambda, then compute optimal weighted mix using half of the
template data, then decode the to-be-decoded data using those weights.

From below: quasi-Newton method of Broyden, Fletcher, Goldfarb, and Shanno (BFGS
~\citep{NoceWrig06}) for optimization. We repeated this
cross-validation process 10 times for each parameter set.

\subsubsection*{Identifying robust decoding results}
Params: Gaussian, Laplace, mexican hat kernels.  Widths of 5, 10, 20,
and 50.

>>>>

\subsubsection*{Feature weighting and testing}
We sought to examine which types of neural features (i.e.,
activations, first-order dynamic correlations, and higher-order
dynamic correlations) were informative to the temporal decoders.
Using the notation above, these features correspond to $\mathbf{Y}_0$,
$\mathbf{X}_1$, $\mathbf{X}_2$, $\mathbf{X}_3$, and so on (we examined
up to tenth order correlations, or $\mathbf{X}_{10}$).

@@

After estimating an optimal set of weights, we computed a new set of
$n + 1$ $\mathbf{\Lambda}$ matrices correlating the DISFC patterns
from $\mathcal{G}_{\mathrm{train}}$ and $\mathcal{G}_{\mathrm{test}}$
at each timepoint.  We use the resulting decoding accuracy of
$\mathcal{G}_{\mathrm{test}}$ timepoints to estimate how informative
the set up neural features containing up to $n^\mathrm{th}$ order
correlations were.

We used a permutation-based procedure to form a stable estimate of
decoding accuracy for each set of neural features.  In particular, we
computed the decoding accuracy for each of 10 random group assignments of
$\mathcal{G}_{\mathrm{train}}$ and $\mathcal{G}_{\mathrm{test}}$.  We
report the mean accuracy (and 95\% confidence intervals) for each set
of neural features.

\subsubsection*{Identifying robust decoding results}
For synthetic data where the true underyling dynamic correlations are
known, we are able to directly evaluate how well the recovered
correlations match the ground truth, for different choices of kernel
shape and width.  For real-world data (where the ground truth is not
known), we use decoding accuracy to estimate whether a given set of
neural features reliably reflects ongoing stimulus-driven cognitive
processing.  We cannot know which choice of kernel most accurately
reflects the ``true'' information content of the data.  For example, a
given kernel might highlight particular temporal aspects of the data
in a way that enhances or diminishes decoding performance.
\textbf{JRM STOPPED HERE}

Params: Gaussian, Laplace, mexican hat kernels.  Widths of 5, 10, 20,
and 50.
